\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[none]{hyphenat}

\renewcommand{\labelitemi}{-}
\setcounter{secnumdepth}{0}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdfauthor={Ockert van Schalkwyk},
    pdftitle={Resume - Ockert van Schalkwyk},
    pdfsubject={Software Developer},
    pdfkeywords={Mendix, JavaScript, Java, Low-code, DID, Digital Wallet}
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

% ─── Header ───────────────────────────────────────────────────────────────────
\section{Ockert van Schalkwyk}
Software Developer \\
Northern Cape, South Africa \\
+27 64 000 6731 \\
\href{mailto:ockert8080@gmail.com}{ockert8080@gmail.com} \\
\href{https://www.linkedin.com/in/ockert-van-schalkwyk-b98b303a5/}{linkedin.com/in/ockert-van-schalkwyk-b98b303a5} \\
\href{https://github.com/otvnvs}{github.com/otvnvs} \\
\href{https://medium.com/@ockert8080}{medium.com/@ockert8080}

% ─── Summary ──────────────────────────────────────────────────────────────────
\section{Summary}

Results-driven Software Developer with over 10 years of experience in rapid web and mobile application development using low-code platforms. Expertise includes complex integrations, custom widgets, digital wallets, decentralized identity solutions, and secure systems across finance, banking, aviation, and digital identity sectors.

% ─── Professional Experience ──────────────────────────────────────────────────
\section{Professional Experience}

\subsection{2025 - 2026: Software Engineer - VMG Labs LLC (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Research and Development; various API integrations. MCP Server and Document Intelligence.
    \item \textbf{Technologies:} Mendix, JavaScript, Java, Python, Groovy, SAP CPI, SAP CAP, VueJS, Azure, Xano.
    \item \textbf{Impact:} Developed a suite of \textbf{rapid prototypes} across diverse use cases to \textbf{drive sales demonstrations}.
\end{itemize}

\subsection{2021 - 2024: Platform Head Engineer - Entidad LLC (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Research and Development; various API integrations. Digital Wallet development; Widget Development; Mentorship.
    \item \textbf{Technologies:} Mendix, JavaScript, Java, Objective-C, React Native.
    \item \textbf{Impact:} Refined \textbf{DID verification} to secure digital wallets, resulting in \textbf{high user adoption}.
\end{itemize}

\subsection{2021: Software Engineer - Inovo Telecoms, Centurion (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} System maintenance and upgrades.
    \item \textbf{Technologies:} Mendix, JavaScript, Java.
    \item \textbf{Impact:} Resolved \textbf{critical legacy system bottlenecks}, ensuring \textbf{high uptime} during maintenance periods.
\end{itemize}

\subsection{2018 - 2021: Software Engineer - Inovo Telecoms, Centurion (Permanent)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Design and implementation of front and back-end processes. Application monitoring solutions; Widget development; Document generation.
    \item \textbf{Technologies:} Mendix, JavaScript, Java, SQL, CSS/LESS/SASS, Python.
    \item \textbf{Impact:} Engineered \textbf{monitoring tools} resulting in enhanced fault detection and \textbf{increased uptime}.
\end{itemize}

\subsection{2018 - 2018: Software Engineer - Teraco Data Environments (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Development and maintenance of front and back-end processes; Widget development.
    \item \textbf{Technologies:} Mendix, JavaScript, CSS/LESS/SASS.
    \item \textbf{Impact:} Optimised \textbf{frontend widgets} to significantly \textbf{elevate agent response times}.
\end{itemize}

\subsection{2015 - 2018: Software Engineer - DocQnet Systems International (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Design, prototype, develop and maintain web applications; Widget development.
    \item \textbf{Technologies:} Mendix, JavaScript, CSS/LESS/SASS, C, C++, Java.
    \item \textbf{Impact:} Developed multiple \textbf{rapid prototypes} across various fields to \textbf{drive sales demonstrations}.
\end{itemize}

\subsection{2014 - 2015: Software Engineer - Software Testing Solutions (Contract)}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Duties:} Front and back-end process implementation; Graphics design.
    \item \textbf{Technologies:} Mendix, JavaScript, CSS/LESS/SASS.
    \item \textbf{Impact:} Enhanced \textbf{UI components} and styling to \textbf{drive client engagement} and resolve recurring defects.
\end{itemize}

% ─── Education ────────────────────────────────────────────────────────────────
\section{Education}

\begin{itemize}[leftmargin=*, noitemsep]
    \item 2009 - 2013: NDip DataMetrics - University of South Africa
    \item 2013 - 2014: Turning and Machining - Kupferberg Engineering Shop
    \item 2003: High School Diploma - Namaqualand High School
\end{itemize}

% ─── Technical Skills ─────────────────────────────────────────────────────────
\section{Technical Skills}

\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Languages:} JavaScript (ES6+), Java, Python, Groovy, C, C++, SQL, HTML5, CSS/SASS/LESS
    \item \textbf{Frameworks \& Platforms:} Mendix (Expert), React Native, VueJS, SAP CAP, Node.js
    \item \textbf{Cloud \& Backend:} Azure, SAP CPI, Xano, Document Intelligence, MCP Server
    \item \textbf{Specialized:} Digital Wallets, Decentralized Identity (DID), API Integrations, Widget Development
\end{itemize}

% ─── Industries ───────────────────────────────────────────────────────────────
\section{Industries}

Finance, Insurance, Credit, Aviation, Governance, Agriculture, IoT, Human Resources, Data Centre, Call Center, Retail, eCommerce, Digital Identity.

% ─── Languages ────────────────────────────────────────────────────────────────
\section{Languages}

English (Fluent) \quad Afrikaans (Mother Tongue)

% ─── References ───────────────────────────────────────────────────────────────
\section{References}

Available upon request.

\end{document}
